Fail Faster

### 2025-03-19 paper/paper.tex
Working on related work
swarm is back baby

\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of each task's speedup, showing that staging leads to better bug-finding ability across the board. As in \todo{earlier figure}, benchmarks with higher numbers of binds (BST (Single-Pass), STLC) see more benefit from staging, whereas benchmarks with more sampling (BST) see a greater speedup from the CSR \rand.}
  \label{fig:etna}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale=0.355]{swarm.png}
  \label{fig:swarm}
  \caption{Histogram of individual-task speedups across different staging strategies and benchmarks. Extreme outliers correspond to large speedups.}
\end{figure}

>>>>

\begin{figure}[h]
  \includegraphics[scale=0.333]{speedup.png}
  \caption{Geometric average of all speedups for each strategy and benchmark, showing that staging leads to better bug-finding ability across the board. As in \todo{earlier figure}, benchmarks with higher numbers of binds (BST (Single-Pass); STLC) see more benefit from staging, whereas benchmarks with more sampling (BST) see a greater speedup from the CSR \rand.}
  \label{fig:etna}
\end{figure}

\begin{figure}[h]
  \includegraphics[scale=0.41]{swarm.png}
  \label{fig:swarm}
  \caption{Distribution of individual-task speedups across strategies and benchmarks. Extreme outliers correspond to large speedups.}
\end{figure}
